Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-25 Paper.tex
Change underscores to spaces in hypertarget captions

\begin{description}
\item[parentHash] The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_p$.
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $H_o$.\hypertarget{beneficiary_H__c}{beneficiary H c}
\item[beneficiary] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_c$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.\hypertarget{receipts_Root_def_words}{receipts_Root_def_words}
\item[receiptsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with the receipts of each transaction in the transactions list portion of the block; formally $H_e$.\hypertarget{logs_Bloom_def_words}{logs Bloom def words}
\item[logsBloom] The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally $H_b$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.\hypertarget{block_number_H_i}{block number H i}
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.\hypertarget{block_gas_used_H__g}{block gas used H g}
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_g$.\hypertarget{block_timestamp_H__s}{block timestamp H s}
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.\hypertarget{block_extraData_H__x}{block extraData H x}
\item[extraData] An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_x$.\hypertarget{mixHash_H__m}{mixHash_H__m}
\item[mixHash] A 256-bit hash which, combined with the nonce, proves that a sufficient amount of computation has been carried out on this block; formally $H_m$.\hypertarget{block_nonce_H__n}{block nonce H n}
\item[nonce] A 64-bit hash which, combined with the mix-hash, proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.\hypertarget{ommer block headers B U}{ommer_block_headers_B__U}\hypertarget{block_B}{block B}
\end{description}

The other two components in the block are simply a list of ommer block headers (of the same format as above) and a series of the transactions. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_H, B_\mathbf{T}, B_\mathbf{U})
\end{equation}\hypertarget{Transaction Receipt}{Transaction_Receipt}

@@

In order to encode information about a transaction concerning which it may be useful to form a zero-knowledge proof, or index and search, we encode a receipt of each transaction containing certain information from concerning its execution.
Each receipt, denoted $B_\mathbf{R}[i]$ for the $i$th transaction, is placed in an index-keyed trie and the root recorded in the header as $H_e$.\hypertarget{transaction_receipt_R}{transaction_receipt_R}\hypertarget{tx_receipt_gas_used_R__u}{tx receipt gas used R u}

>>>>

\begin{description}
\item[parentHash] The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_p$.
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $H_o$.\hypertarget{beneficiary_H__c}{beneficiary H c}
\item[beneficiary] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_c$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.\hypertarget{receipts_Root_def_words}{receipts Root def words}
\item[receiptsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with the receipts of each transaction in the transactions list portion of the block; formally $H_e$.\hypertarget{logs_Bloom_def_words}{logs Bloom def words}
\item[logsBloom] The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally $H_b$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.\hypertarget{block_number_H_i}{block number H i}
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.\hypertarget{block_gas_used_H__g}{block gas used H g}
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_g$.\hypertarget{block_timestamp_H__s}{block timestamp H s}
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.\hypertarget{block_extraData_H__x}{block extraData H x}
\item[extraData] An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_x$.\hypertarget{mixHash_H__m}{mixHash H m}
\item[mixHash] A 256-bit hash which, combined with the nonce, proves that a sufficient amount of computation has been carried out on this block; formally $H_m$.\hypertarget{block_nonce_H__n}{block nonce H n}
\item[nonce] A 64-bit hash which, combined with the mix-hash, proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.\hypertarget{ommer block headers B U}{ommer_block_headers_B__U}\hypertarget{block_B}{block B}
\end{description}

The other two components in the block are simply a list of ommer block headers (of the same format as above) and a series of the transactions. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_H, B_\mathbf{T}, B_\mathbf{U})
\end{equation}\hypertarget{Transaction Receipt}{Transaction Receipt}

@@

In order to encode information about a transaction concerning which it may be useful to form a zero-knowledge proof, or index and search, we encode a receipt of each transaction containing certain information from concerning its execution.
Each receipt, denoted $B_\mathbf{R}[i]$ for the $i$th transaction, is placed in an index-keyed trie and the root recorded in the header as $H_e$.\hypertarget{transaction_receipt_R}{transaction receipt R}\hypertarget{tx_receipt_gas_used_R__u}{tx receipt gas used R u}
